VitalLens 1.0 Technical Report

### 2023-12-06 paper.tex
Demographics figures

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{pgfplots}
\usepackage{subcaption}

@@

\paragraph{Participant diversity.}
The skin type diversity of PROSIT is lacking, with too many type 2 and too few type 5 and 6 participants.
This is why we additionally use the Vital Videos Ghana training set when training our model.

TODO: Histogram of ages x n participants

\begin{figure}[h!]
    \centering
    \begin{subfigure}{0.48\textwidth}
    	\centering
    	\begin{tikzpicture}
        	\begin{axis}[
            		table/col sep=comma,
            		ybar,
            		ylabel=Frequency,
            		xlabel={Heart rate [bpm]},
            		xmin=35,
            		xmax=130,
            		width=\textwidth,
            		height=5cm,
            		grid=major,
            		bar width=12pt
            	]
            	\addplot[fill=red!60,opacity=0.8] table[x index=0, y index=1] {hr_histogram.csv};
        	\end{axis}
    	\end{tikzpicture}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.48\textwidth}
    	\centering
    	\begin{tikzpicture}
        	\begin{axis}[
            		table/col sep=comma,
            		ybar,
            		ylabel=Frequency,
            		xlabel={Respiratory rate [rpm]},
            		xmin=-2,
            		xmax=40,
            		width=\textwidth,
            		height=5cm,
            		grid=major,
            		bar width=12pt
            	]
            	\addplot[fill=blue!60,opacity=0.8] table[x index=0, y index=1] {rr_histogram.csv};
        	\end{axis}
    	\end{tikzpicture}
    \end{subfigure}
	\begin{subfigure}{0.48\textwidth}
    	\centering
    	\begin{tikzpicture}
        	\begin{axis}[
            		table/col sep=comma,
            		ybar,
            		ylabel=Frequency,
            		xlabel={Blood pressure [mmHg]},
            		xmin=50,
            		xmax=170,
            		width=\textwidth,
            		height=5cm,
            		grid=major,
            		legend style={at={(.98,.97)}, anchor=north east},
            	]
            	\addplot[ybar,bar width=10pt,fill=blue!60,opacity=0.8] table[x index=0, y index=1] {bp_sys_histogram.csv};
            	\addlegendentry{SBP}
            	\addplot[ybar,bar width=7pt,fill=red!60,opacity=0.7] table[x index=0, y index=1] {bp_dia_histogram.csv};
            	\addlegendentry{DBP}
        	\end{axis}
    	\end{tikzpicture}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.48\textwidth}
    	\centering
    	\begin{tikzpicture}
        	\begin{axis}[
            		table/col sep=comma,
            		ybar,
            		ylabel=Frequency,
            		xlabel={SpO2 [\%]},
            		xmin=87,
            		xmax=101,
            		width=\textwidth,
            		height=5cm,
            		grid=major,
            		bar width=12pt
            	]
            	\addplot[fill=blue!60,opacity=0.8] table[x index=0, y index=1] {spo2_histogram.csv};
        	\end{axis}
    	\end{tikzpicture}
    \end{subfigure}
    \caption{Distributions of chunk summary vitals in PROSIT}
    \label{fig:histogram}
\end{figure}

TODO: Histogram of skin types x n participants
TODO: Histogram of genders x n participants1

\paragraph{Vitals diversity.}
There are also several participants who have an irregular heartbeat.

TODO: Histogram of HR x n chunks
TODO: Histogram of RR x n chunks
TODO: Histogram of BP x n chunks
TODO: Histogram of SpO2 x n chunks

\subsection{Vital Videos}

@@

\section{Results and Discussion}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{pgfplots}
\usepackage{subcaption}
\usepackage{csvsimple}

@@

\paragraph{Participant diversity.}
The demographics of the participants in PROSIT are given in Figure \ref{fig:prosit-demographics}.
Most participants in PROSIT are under 40 years old, and there are more male than female participants.
As we show in Section \ref{results}, this is not an issue in practice.
However, the skin type diversity of PROSIT is also lacking, with too many type 2 and too few type 5 and 6 participants.
This is in fact an issue.
To avoid a skin type bias in our model, we supplement our training data with the \textit{Vital Videos Ghana} training set which has mostly type 5 and 6 participants.

% Modified example from www.texample.net for pie charts
% This example needs the packages tikz, xcolor, calc
\definecolorseries{myseries}{rgb}{step}[rgb]{.95,.85,.55}{.17,.47,.37}
\resetcolorseries{myseries}%

% a pie slice
\newcommand{\slice}[4]{
	\pgfmathsetmacro{\midangle}{0.5*#1+0.5*#2}
	\begin{scope}
		\clip (0,0) -- (#1:1) arc (#1:#2:1) -- cycle;
		\colorlet{SliceColor}{myseries!!+}%
		\fill[inner color=SliceColor!30,outer color=SliceColor!60] (0,0) circle (1cm);
	\end{scope}
	\draw[thick] (0,0) -- (#1:1) arc (#1:#2:1) -- cycle;
	\node[label={[font=\small]\midangle:#4}] at (\midangle:1) {};
	\pgfmathsetmacro{\temp}{min((#2-#1-10)/110*(-0.3),0)}
	\pgfmathsetmacro{\innerpos}{max(\temp,-0.5) + 0.8}
	\node[font=\small] at (\midangle:\innerpos) {#3};
}

\begin{figure}[h!]
	\centering
    \begin{subfigure}{0.32\textwidth}
    	\centering
    	\begin{tikzpicture}
        	\begin{axis}[
            		table/col sep=comma,
            		ybar,
            		xmin=10,
            		xmax=95,
            		ylabel=Frequency,
            		width=\textwidth,
            		height=4.6cm,
            		grid=major,
            		bar width=8pt,
            		y label style={yshift=-12pt},
            		label style={inner sep=0pt}
            	]
            	\addplot[fill=blue!60,opacity=0.8] table[x index=0, y index=1] {data/age_histogram.csv};
        	\end{axis}
    	\end{tikzpicture}
    	\caption{Age}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
    	\centering
    	% drawing of the pie chart
    	\begin{tikzpicture}[scale=1.5]%
    	\def\mya{0}\def\myb{0}
    	\csvreader[before reading=\def\mysum{0}]{data/gender.csv}{Value=\Value}{%
			\pgfmathsetmacro{\mysum}{\mysum+\Value}%
		}
		\csvreader[head to column names]{data/gender.csv}{}{%
			\let\mya\myb
			\pgfmathsetmacro{\myb}{\myb+\Value}
			\slice{\mya/\mysum*360}{\myb/\mysum*360}{\Value}{\Label}
		}
		\end{tikzpicture}%
		\caption{Gender}
    \end{subfigure}
    \begin{subfigure}{0.32\textwidth}
    	\centering
    	% drawing of the pie chart
    	\begin{tikzpicture}[scale=1.5]%
    	% sum of amounts
		\csvreader[before reading=\def\mysum{0}]{data/gender.csv}{Value=\Value}{%
			\pgfmathsetmacro{\mysum}{\mysum+\Value}%
		}
    	\def\mya{0}\def\myb{0}
		\csvreader[head to column names]{data/skin_type.csv}{}{%
			\let\mya\myb
			\pgfmathsetmacro{\myb}{\myb+\Value}
			\slice{\mya/\mysum*360}{\myb/\mysum*360}{\Value}{\Label}
		}
		\end{tikzpicture}%
		\caption{Skin type}
    \end{subfigure}
    \hfill
    \caption{Participant demographics in PROSIT}
    \label{fig:prosit-demographics}
\end{figure}

\paragraph{Vitals diversity.}
Distributions of the vitals in PROSIT are given in Figure \ref{fig:prosit-vitals-histogram}.
The participants are mostly healthy, so these vitals fall in the typical ranges.
There are several participants who have an irregular heartbeat.

\begin{figure}[h!]
    \centering
    \begin{subfigure}{0.48\textwidth}
    	\centering
    	\begin{tikzpicture}
        	\begin{axis}[
            		table/col sep=comma,
            		ybar,
            		ylabel=Frequency,
            		xlabel={Heart rate [bpm]},
            		xmin=35,
            		xmax=130,
            		width=\textwidth,
            		height=5cm,
            		grid=major,
            		bar width=12pt
            	]
            	\addplot[fill=red!60,opacity=0.8] table[x index=0, y index=1] {data/hr_histogram.csv};
        	\end{axis}
    	\end{tikzpicture}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.48\textwidth}
    	\centering
    	\begin{tikzpicture}
        	\begin{axis}[
            		table/col sep=comma,
            		ybar,
            		ylabel=Frequency,
            		xlabel={Respiratory rate [rpm]},
            		xmin=-2,
            		xmax=40,
            		width=\textwidth,
            		height=5cm,
            		grid=major,
            		bar width=12pt
            	]
            	\addplot[fill=blue!60,opacity=0.8] table[x index=0, y index=1] {data/rr_histogram.csv};
        	\end{axis}
    	\end{tikzpicture}
    \end{subfigure}
	\begin{subfigure}{0.48\textwidth}
    	\centering
    	\begin{tikzpicture}
        	\begin{axis}[
            		table/col sep=comma,
            		ybar,
            		ylabel=Frequency,
            		xlabel={Blood pressure [mmHg]},
            		xmin=50,
            		xmax=170,
            		width=\textwidth,
            		height=5cm,
            		grid=major,
            		legend style={at={(.98,.97)}, anchor=north east},
            	]
            	\addplot[ybar,bar width=10pt,fill=blue!60,opacity=0.8] table[x index=0, y index=1] {data/bp_sys_histogram.csv};
            	\addlegendentry{SBP}
            	\addplot[ybar,bar width=7pt,fill=red!60,opacity=0.7] table[x index=0, y index=1] {data/bp_dia_histogram.csv};
            	\addlegendentry{DBP}
        	\end{axis}
    	\end{tikzpicture}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.48\textwidth}
    	\centering
    	\begin{tikzpicture}
        	\begin{axis}[
            		table/col sep=comma,
            		ybar,
            		ylabel=Frequency,
            		xlabel={SpO2 [\%]},
            		xmin=87,
            		xmax=101,
            		width=\textwidth,
            		height=5cm,
            		grid=major,
            		bar width=12pt
            	]
            	\addplot[fill=blue!60,opacity=0.8] table[x index=0, y index=1] {data/spo2_histogram.csv};
        	\end{axis}
    	\end{tikzpicture}
    \end{subfigure}
    \caption{Distributions of chunk summary vitals in PROSIT}
    \label{fig:prosit-vitals-histogram}
\end{figure}
\subsection{Vital Videos}

@@

\section{Results and Discussion}
\label{results}
